---
title: "Task1"
output: html_document
date: "2022-11-29"
---

## Task 1

1. Create variables with all atomic types. Atomic types: `character`, `numeric`, `integer`, `complex`, `logical`.
```{r}
ch <- "Car"
nu <- 5
int <- 56L
co <- 67+8
lo <- TRUE

list(ch, nu, int, co, lo)

```



2. Create the next vectors:
  * sequence from 5 to 75;
  * numbers: 3.14, 2.71, 0, 13;
  * with 100 `TRUE` values.

```{r}
5:75
c(3.14, 2.71, 0, 13)
v3 = rep(c(TRUE), each=100)
print(v3)


```


3. Create the next matrix:

|  |   |  |
|:---:|:-----:|:---:|
| 12  | 34    | 87  |
| -12 | -12.1 | 0   |
| 3.6 | 0.5   | 1.3 |
```{r}
exp_matrix <- matrix(list(12,-12,3.6,34,-12.1,0.5,87,0,1.3), nrow = 3, ncol = 3)
print(exp_matrix)
```

4. Create a `list` with all atomic types.
```{r}
numeric <- 1.5
integer <- 100L
complex <- 2+2i
character <- "Character/String"
logical <- TRUE

atomic_type_example_list <- list(numeric, integer, complex, character, logical)
print(atomic_type_example_list)

atomic_types <- list(typeof(numeric), typeof(integer), typeof(complex), typeof(character), typeof(logical))
print(atomic_types)
```

5. Create a `factor` with 3 levels: `infant`, `child`, `adult`.
```{r}
three_level_factor <- factor(c("infant", "child", "adult"))
print(three_level_factor)

```


6. Create a `data frame`
```{r}
Data_Frame <- data.frame (Player = c("Lenka", "Romanka", "Pepa"), Games_Played = c(8, 10, 6), Points = c(20,30,24))
```

7. Change column names of the `data frame`.
```{r}
colnames(Data_Frame) <- c("Hraci", "Odohrate_Zapasy","Body")
print(Data_Frame)
```
Q1- The column names are: (Key/Index), Ozone, Solar.R, Wind, Temp, Month, Day

library(dplyr)

```{r}
column_names <- names(airquality)
print("Question 1 - Print Data Frame Column Names: ")
print(column_names)


```

Q2 - What are the row names of the data frame?
Row names are basically the index/key of each entry

```{r}
row_names <- row.names(airquality)
print("Question 2 - Print Data Frame Row Names: ")
print(row_names)
print("As you can see, row names simply represent the keys/index of each entry")
```

Q3 - Extract the first 6 rows of the data frame and print them to the console

```{r}
first_six <- head(airquality)
print("Question 3 - Extract first 6 rows: ")
print(first_six)
```

Q4 - How many observations (i.e. rows) are in this data frame?

```{r}
row_num <- nrow(airquality)
print("Question 4 - How many observations/rows does the dataframe hold: ")
print(row_num)
```

Q5 - Extract the last 6 rows of the data frame and print them to the console

```{r}
last_six <- tail(airquality)
print("Question 5 - Extract last 6 rows: ")
print(last_six)
```

Q6-7 - For questions 6 and 7 we can use the helpful summary function

```{r}
ozone_summary <- summary(airquality$Ozone)
###Summary function prints different information relevant to specified column ozone
print("This prints a detailed summary of the specified attribute/column -- Ozone")
print(ozone_summary)
```

Q6 - How many missing values are in the “Ozone” column of this data frame?
Since we are interested in missing values (NA's) - we specify position 

```{r}
print("Question 6 - Print number of missing values/NA's in Ozone attribute/column:  ")
print(ozone_summary[7])
```

Q7 - What is the mean of the “Ozone” column in this dataset? Exclude missing values (coded as NA) from this calculation

```{r}
print("Question 7 - Mean value of Ozone attribute/columnL ")
print(ozone_summary[4])
```

Q8 - Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90.

```{r}
que8 <- subset(airquality, airquality$Ozone > 31 & airquality$Temp > 90)
print("Question 8 - Print subset of rows where Ozone vals are above 31 and Temperature vals are abov 90: ")
print(que8)
```







